Topological Sigma Models for Generalized Para-Complex Geometry

### 2019-12-21 newdraft.tex
added holo. volume form

Similarly, the cotangent bundle is a holomorphic bundle. For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles. The {\bf para-complex Dolbeault complex} is therefore given by
\begin{align}
\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{\bullet,0},\pd\right).
\end{align}
\brian{Should this be the thing resolving paraholomorphic functions or anti paraholomorphic functions? If paraholomorphic it should be $\mathbf{\Omega}^{0,\bullet}$. }
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

@@

\brian{Can we import some of the other examples here?
Maybe some explicit ones like the toric fibrations you mentioned.}

@@

\paragraph{Expanding the $(1,1)$ action}
We now expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
%In components, the superfield has the form
%\[
%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
%\]
%The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
\[
D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp,
\]
and
\begin{align*}
[\eta(\Phi)+b(\Phi)]_{ij} = & [\eta(\phi)+b(\phi)]_{ij}+\p_k[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
& +\frac{1}{2}\p_k\p_l[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
\end{align*}
After plugging the above in the action and performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients. From this we find that
%\begin{align*}
%\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
%&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
%&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
%\end{align*}
the field $F$ enters only algebraically and not via its derivatives. Therefore, it is auxiliary and can be integrated out. To obtain the equations of motion for $F$,
%we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
%\begin{align*}
%g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
%+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
%\end{align*}
%Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
%\begin{align*}
%g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
%\end{align*}
%where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
we vary the resulting bosonic action with respect to $F^i$:
\begin{align} \label{F_EoM}
\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+.
\end{align}
Here, $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}\eta^{-1}H$.
\david{we can show more of the calculations or put some more in the appendix but this is fairly standard knowledge and I think the above is sufficient}
\subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
We continue by extending the above $(1,1)$ picture to the $(2,2)$ para-SUSY setting. This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.

@@

\david{is the following paragraph needed?}
\brian{I think it's nice to point out how it  generalizes.}

>>>>

Similarly, the cotangent bundle is a holomorphic bundle. For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles. The {\bf para-complex Dolbeault complex} is therefore given by
\begin{align}\label{para-dolbeault}
\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{0,\bullet},\pd\right).
\end{align}

%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}
\paragraph{The para-holomorphic volume form}
In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds. Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.

Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{k,0}(M)$, that is holomorphic, $\bar{\p}\Omega=0$. Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
\begin{Def}
Let $(\PS,K)$ be a para-complex manifold of dimension $2n$. We define a para-holomorphic volume form to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
\begin{align*}
\pt \Omega=\p \tl{\Omega}=0.
\end{align*}
\end{Def}
Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.

@@

@@

\paragraph{Expanding the $(1,1)$ action}
We now expand the action \eqref{eq:(1,1)action} by plugging in \eqref{fields_(1,1)} and \eqref{eq:D1}. The expansions read
%In components, the superfield has the form
%\[
%\Phi^i =\phi^i+\theta^+\psi^i_++\theta^-\psi^i_-+\theta^+\theta^-F^i
%\]
%The super covariant derivatives $D_{\pm}$ applied to $\Phi^i$ read
\[
D_\pm\Phi^i =\psi^i_\pm\pm\theta^\mp F^i-\theta^\pm\p_\pm\phi^i\mp\theta^+\theta^-\p_\pm\psi^i_\mp,
\]
and
\begin{align*}
[\eta(\Phi)+b(\Phi)]_{ij} = & [\eta(\phi)+b(\phi)]_{ij}+\p_k[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k+\theta^+\theta^-F^k)\\
& +\frac{1}{2}\p_k\p_l[\eta(\phi)+b(\phi)]_{ij}(\theta^+\psi_+^k+\theta^-\psi_-^k)(\theta^+\psi_+^l+\theta^-\psi_-^l).
\end{align*}
After plugging the above in the action and performing the odd integration, the only terms that survive are the $\theta^+\theta^-$ coefficients. From this we find that
%\begin{align*}
%\theta^+\theta^-&\left[(g+b)_{ij}(\psi_+^i\p_-\psi^j_++\psi^j_-\p_-\psi^i_-+F^iF^j+\p_+\phi^i\p_-\phi^j)\right. \\
%&+\p_k(g+b)_{ij}\left(F^k\psi^i_+\psi^j_-+\psi^k_+(-F^i\psi^j_--\psi^i_+\p_-\phi^j)+\psi^k_-(-\p_+\phi^i\psi^j_-+\psi_+^iF^j)\right)\\
%&\left. +\frac{1}{2}\p_k\p_l(g+b)_{ij}(-\psi_+^k\psi_-^l\psi_+^i\psi_-^j+\psi_-^k\psi_+^l\psi^i_+\psi^j_-) \right].
%\end{align*}
the field $F$ enters only algebraically and not via its derivatives. Therefore, it is auxiliary and can be integrated out. To obtain the equations of motion for $F$,
%we use the formula $\p_kg_{ij}=\Gamma_{ikj}+\Gamma_{jki}$ and collect the terms involving $F$:
%\begin{align*}
%g_{ij}F^iF^j+&(\Gamma_{ikj}+\Gamma_{jki})(F^k\psi^i_+\psi^j_--F^i\psi^k_+\psi^j_-+F^j\psi^k_-\psi_+^i)\\
%+&F^k\psi^i_+\psi^j_-(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki}).
%\end{align*}
%Using $\Gamma_{ikj}=\Gamma_{kij}$ and $H_{ijk}=(\p_kb_{ij}+\p_ib_{jk}+\p_jb_{ki})$, we can rewrite this as
%\begin{align*}
%g_{ij}F^iF^j+2\Gamma_{ikj}F^j\psi^k_-\psi_+^i+F^k\psi^i_+\psi^j_-H_{ijk}=g_{ij}(F^iF^j+2F^j(\Gamma^-)_{lk}^i\psi_-^k\psi_+^l),
%\end{align*}
%where $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}g^{-1}H$. This yields the equation of motion for $F$,
we vary the resulting bosonic action with respect to $F^i$:
\begin{align} \label{F_EoM}
\frac{\delta S_{(1,1)}}{\delta F^i}=0\quad \Longleftrightarrow\quad  F^i=-(\Gamma^-)^i_{jk}\psi^k_-\psi^j_+.
\end{align}
Here, $\Gamma^-$ are the Christoffel symbols of the connection $\n^-=\lc-\frac{1}{2}\eta^{-1}H$.

\subsection{$(2,2)$ para-supersymmetry}\label{sec:(2,2)parasusy}
We continue by extending the above $(1,1)$ picture to the $(2,2)$ para-SUSY setting. This version of supersymmetry and the corresponding sigma models were first discussed in \cite{HullTwistedSUSY}.

@@
